The Unicode Cookbook \linebreak for Linguists

### 2018-06-05 book/chapters/implementation.tex
deals with paperhivers for chapter 8

Given a set of graphemes, there are at least two different methods to tokenize
strings. The first is called \texttt{method = "global"}. This approach
takes the first grapheme in the profile, then matches this grapheme globally at
all places in the string, and then turns to the next string in the profile. The 
other approach is called \texttt{method = "linear"}. This
approach walks through the string from left to right. At the first character it
looks through all graphemes whether there is any match, and then walks further
to the end of the match and starts again. This approach is more akin to
finite-state rewrite rules (though note that it still works differently from
such rewrite rules, see above). The global method is used 
by default in the R implementation.

@@

Further, the current R-implementation has a limitation when regular expressions
are used. The problem is that overlapping matches are not captured when using
regular expressions.\footnote{This restriction is an effect of the underlyingly
used ICU implementation of the Unicode Standard as implemented in R through the
package \textttf{stringi}.} Everything works as expected without regular
expressions, but there might be warnings/errors in case of \texttt{regex =
TRUE}. However, just as in the previous issue, this problem should only very
rarely (when at all) happen in natural language data.

@@

Online we provide several use cases -- what we refer to as recipes -- that illustrate the applications of orthography profiles using our implementations in Python and R.\footnote{\url{https://github.com/unicode-cookbook/recipes}} Here we briefly describe these use cases and we encourage users to try them out using Git and Jupyter Notebooks.

@@

\noindent The ASJP use case shows how to download the full set of ASJP wordlists, to combine them into a single large CSV file, and to tokenize the ASJP orthography. The Dutch use case takes as input the 10K corpus for Dutch (``nld'') from the Leipzig Corpora Collection,\footnote{\url{http://corpora2.informatik.uni-leipzig.de/download.html}} which is then cleaned and tokenized with an orthography profile that captures the intricacies of Dutch orthography.

>>>>

Given a set of graphemes, there are at least two different methods to tokenize
strings. The first is called \texttt{method = "global"}. This approach
takes the first grapheme in the profile, then matches this grapheme globally at
all places in the string, and then turns to process the next string in the profile. The 
other approach is called \texttt{method = "linear"}. This
approach walks through the string from left to right. At the first character it
looks through all graphemes whether there is any match, and then walks further
to the end of the match and starts again. This approach is more akin to
finite-state rewrite rules (though note that it still works differently from
such rewrite rules, as previously stated). The global method is used 
by default in the R implementation.

@@

Further, the current R implementation has a limitation when regular expressions
are used. The problem is that overlapping matches are not captured when using
regular expressions.\footnote{This restriction is an effect of the underlyingly
used ICU implementation of the Unicode Standard as implemented in R through the
package \textttf{stringi}.} Everything works as expected without regular
expressions, but there might be warnings/errors in case of \texttt{regex =
TRUE}. However, just as in the previous issue, this problem should only very
rarely (when at all) happen in natural language data.

@@

We provide several use cases online -- what we refer to as \textit{recipes} -- that illustrate the applications of orthography profiles using our implementations in Python and R.\footnote{\url{https://github.com/unicode-cookbook/recipes}} Here we briefly describe these use cases and we encourage users to try them out using Git and Jupyter Notebooks.

@@

\noindent The ASJP use case shows how to download the full set of ASJP wordlists, to combine them into a single large CSV file, and to tokenize the ASJP orthography. The Dutch use case takes as input the 10K corpus for Dutch (``nld'') from the Leipzig Corpora Collection,\footnote{\url{http://wortschatz.uni-leipzig.de/en/download/}} which is then cleaned and tokenized with an orthography profile that captures the intricacies of Dutch orthography.
